Rank verification for exponential families

### 2016-04-09 verifying-winner.tex
Correction factor for alpha included in Matlab code; Diagrams updated / added in paper

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}

@@

We often make observations that form a joint exponential family distribution. While it might be relatively obvious in the independent case, the observations can well be dependent and hinge on the natural parameters. Comparison of these natural parameters can produce useful inferences.

@@

\begin{equation}
\PP_F\left(\text{reject } H_0\right) = \sum_{j \text{ is a candidate}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
\label{eqn:marginal_error}
\end{equation}

@@

We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
$$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate given in \Cref{eqn:marginal_error} at $\alpha$ too.

@@

Suppose we observe
$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(N, \pi\right)$$
and we want to test
$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
$$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
The distribution, written in an exponential family format, is
$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = N}}{X_1! \cdots X_n!}.$$

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n \log \pi_n = N}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
$$\frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t} \left(\frac{1}{2}\right)^{X_1 + X_j}} = \frac{\sum_{t = X_1}^{X_1 + X_j} \binom{X_1 + X_j}{t}}{\sum_{t = \left(X_1 + X_j\right)/2}^{X_1 + X_j} \binom{X_1 + X_j}{t}},$$
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/m$ where $m$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / N$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / N$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This was achieved by finding an integer $D$, as a function on $N$ and $n$, and select by
$$J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\}.$$
Gupta and Nagel also provided the method to choose $D$, which we implemented.

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(N, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $N$ and $n$. The two procedure coincide if $n = 2$ as there are is actual selection. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth, trim = {1.3in 0.7in 1.6in 0.6in}, clip]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $N = 50$ and the second row $N = 250$. The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
\label{fig:power}
\end{figure}

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the distribution is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we define the notion of {\em majorization}.

@@

Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
\begin{align*}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz}
\end{align*}

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
	\draw[->, thick] (-2, 1) -- (6, -3);
	\draw[->, thick] (-3, -2) -- (6, 4);
	\fill (0, 0) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{13}, X_2, M_{13}\right)$};
	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (5, -2.5) -- (5, 10/3) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these rays, that lie on a level set of $x_1 + x_2 + x_3$. The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}. The dotted lines with the majorization symbols show the majorization relation between vectors on the two rays.}
\label{fig:rays}
\end{figure}

We can re-parametrize this further, thanks to some geometric intuition (ref.\ \Cref{fig:rays}) that both $p$-values are actually integrals of $g$ along intersecting rays. We have
\begin{align}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \nonumber \\
& \ge \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \label{eqn:int_extension} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz} \label{eqn:p13}
\end{align}

Indeed from the second point \Cref{lma:two_properties} we have
$$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$ and the majorization reversed for $z \ge 0$. So Schur-concavity shows that
$$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$, and the inequality reversed for $z \ge 0$. Consequently, $p_{12} \ge p_{13}$ by comparing \Cref{eqn:int_extension,eqn:p13}.

@@

The same argument in \Cref{fig:rays} shows that $p_{12} \ge p_{13}$. This is again true for the case where $X_2 \ge M_{13}$ as well. This means that the bound can be constructed considering only $p_{12}$.

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\draw[dashed, thick] (-3, 1.5) -- (-2, 1);
	\draw[thick] (-2, 1) -- (5, -2.5);
	\draw[thick] (-3, -2) -- (5, 10/3);
	\fill (0, 0) circle(2pt) node[right] {$\left(X_j, X_{j+1}, X_k\right)$};
	\fill (-2, 1) circle(2pt) node[above right] {$\left(M_{j\left(j+1\right)}, M_{j\left(j+1\right)}, X_k\right)$};
	\fill (-3, -2) circle(2pt) node[below] {$\left(M_{jk}, X_{\left(j+1\right)}, M_{jk}\right)$};
	\fill (-3, 1.5) circle(2pt) node[above] {$\left(M_{jk}, X_{j+1} + D_{jk}, X_k\right)$};
	\draw[dotted, thick] (-3, 1.5) -- (-3, -2) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (-2, 1) -- (-2, -4/3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (3, -1.5) -- (3, 2) node[midway, above, rotate=-90] {$\succeq$};
	\draw[dotted, thick] (5, -3) -- (5, 4) node[midway, above, rotate=-90] {Truncation for $X_j < X_{j-1}$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extending the integral in the denominator of \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:exponential_families}. The upper truncation for $X_j$ can be represented by cropping \Cref{fig:rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning. Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.

@@

\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = N\right\}}}{x_1! \cdots x_n!}$$
Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters. Note that the multinomial coefficient is naturally Schur-concave. The step-down procedure is applied to verify the position of the other candidates. Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$. We summarize the test in \Cref{tbl:poll_analysis}.

>>>>

\documentclass[11pt]{article}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{caption}
\usepackage{cleveref}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[totalwidth=480pt, totalheight=680pt]{geometry}
\usepackage{mathrsfs}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{xcolor}

@@

We often make observations that form a joint distribution. While it might be relatively obvious in the independent case, the observations can well be dependent, complicating comparisons of parameters. However, comparison of these parameters can produce useful inferences.

@@

\begin{equation}
\PP_F\left(\text{reject } H_0\right) = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right).
\label{eqn:marginal_error}
\end{equation}

@@

We will construct a test as outlined by Fithian, Sun and Taylor in \cite{Fithian:2014ws}. The fundamental idea is to consider the selective type I error rate
$$\PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls} \right), ~~~~~~~~ \text{where $j$ is a candidate,}$$
instead. Note that controlling this selective type I error rate at $\alpha$ provides control of the marginal type I error rate at $\alpha$ too. From \Cref{eqn:marginal_error},
\begin{align}
\PP_F\left(\text{reject } H_0\right) & = \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \PP_F\left(\text{reject } H_0 \middle| j \text{ leads in polls}\right) \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
& \le \sum_{\substack{j \text{ is a candidate} \\ j \text{ does not have most support}}} \alpha \PP_F \left(j \text{ leads in polls}\right). \nonumber \\
& = \alpha \PP\left(\text{Leader in polls does not have most support}\right) \nonumber \\
& \le \frac{n-1}{n} \alpha. \label{eqn:selective_vs_marginal}
\end{align}

@@

Suppose we observe
$$\left(X_1, \ldots, X_n\right) \sim \text{Multinomial}\left(m, \pi\right)$$
and we want to test
$$H_{0j}: \pi_j \le \max_{k \ne j} \pi_k = \bigcup_{k \ne j} H_{0jk}: \pi_j \le \pi_k$$
when $X_j$ is larger than all other $X_k$. To break ties, we introduce independent auxiliary random variable $U_j \sim U\left[0,1\right]$, and opt to test $H_{0j}$ in the event of
$$A_j = \left\{X_j + U_j > \max_{k \ne j} X_k + U_k\right\}.$$
The distribution, written in an exponential family format, is
$$\exp\left(X_1 \log \pi_1 + \cdots + X_n \log \pi_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Without loss of generality, we will assume $X_1$ is considered largest with the tie-breaking method above in mind. Following the construction in \cite{Fithian:2014ws}, if we want to construct $p$-values $p_{1j}$ for $H_{01j}$, we need to first re-parametrize such that the selection event $A_1$ can be expressed as the sufficient statistic. The distribution is now
$$\exp\left(\frac{X_1 - X_j}{2} \left(\log \pi_1 - \log \pi_j\right) + \cdots + \frac{X_1 + X_j}{2} \left(\log \pi_1 + \log \pi_j\right) + \cdots + X_n\right) \frac{1_{X_1 + \cdots + X_n = m}}{X_1! \cdots X_n!}.$$

Next we condition on the sufficient statistics that are multiplied to the the nuisance parameter, in other words, we consider the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(\frac{X_1 - X_j}{2} \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
or equivalently, the conditional law
$$\mathcal{L}_{\pi_1 = \pi_j}\left(X_1 \middle| X_2, \ldots, \frac{X_1 + X_j}{2}, \ldots, X_n, A_1\right),$$
which is the distribution $\text{Binomial}\left(X_1 + X_j, \frac{1}{2}\right)$ truncated by the event $A_1$. The one-sided $p$-value $p_{1j}$ is thus given as
\begin{align*}
p_{ij}\left(x_1, \ldots, x_n\right) & = \PP\left(X_1 \ge x_1 \middle| X_2 = x_2, \ldots, \frac{X_1 + X_j}{2} = \frac{x_1 + x_j}{2}, \ldots, X_n = x_n, A_1\right) \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t} \left(\frac{1}{2}\right)^{x_1 + x_j}} \\
& = \frac{\sum_{t = x_1}^{x_1 + x_j} \binom{x_1 + x_j}{t}}{\sum_{t = \left(x_1 + x_j\right)/2}^{x_1 + x_j} \binom{x_1 + x_j}{t}},
\end{align*}
and to account for the tie-breaking we adopted earlier, we
\begin{itemize}
\item multiply the first term in the numerator and the numerator by $1/k$ where $k$ is the number of observations tied for largest; otherwise,
\item multiply the first term in the denominator by $1/2$ if $X_1$ and $X_2$ has the same parity.
\end{itemize}
Noticing that if there are ties for the largest the $p$-value is $1$ and the denominator is really $1/2$ otherwise, we can write
$$p_{1j} = 1 \wedge 2 \sum_{t=X_1}^{X_1 + X_j} \binom{X_i + X_j}{t}.$$

@@

It may appear quite surprising that ``verifying a winner'' as we propose in this section requires no adjustment for multiplicity, in the sense that we only need to compare the winner to the runner- up, just as we would have done if $n = 2$. After all, we know that the winner suffer’s from a winner's curse: given $X_5$ is the winner, $X_5 / m$ would overestimate $\pi_5$, and the larger $n$ is, the more severe this bias is likely to be. However, if $X_9$ is the runner-up, then $X_9 / m$ is likely biased upward nearly as much as $X_5$. Informally, we might say that $X_9$ suffer’s from a “runner-up’s curse” that is nearly as bad as the winner's curse; as a result, $X_5 - X_9$ is actually not all that biased upward. By multiplying the $p$-value by $2$, or equivalently performing a two-tailed test, takes care of what little bias there is. Indeed, performing a two-tailed test can be viewed as a sort of ``correction for multiplicity'', albeit one that we would have to make even if $n = 2$.

@@

Gupta and Nagel \cite{Gupta:1967wg} devised a rule to select a subset that includes the maximum $\pi_j$. In other words, if the selected subset is $J\left(X\right)$, they guaranteed
$$\PP\left(\argmax_j \pi_j \in J\left(X\right)\right) \ge 1 - \alpha.$$
This was achieved by finding an integer $D$, as a function on $m$, $n$ and $\alpha$, and select by
\begin{equation}
J\left(X\right) = \left\{j: X_j \ge \max_k X_k - D\right\} \tag{Procedure GN}.
\label{eqn:gn}
\end{equation}
Gupta and Nagel also provided the method to choose $D$, which we implemented.

\Cref{fig:power} gives the power curves for $\text{Multinomial}\left(m, \pi\right)$ and
$$\pi \propto \left(e^\delta, 1, \ldots, 1\right),$$
for various combinations of $m$ and $n$. For \ref{eqn:gn}, we use $\alpha = 0.05$; but to account for the extra factor of $\frac{n-1}{n}$ in \Cref{eqn:selective_vs_marginal}, we will apply the selective procedure for with $\frac{n}{n-1} \alpha$ such that the marginal type I error rate for both procedures is controlled at $\alpha$. \ref{eqn:gn} coincides with our test at $n = 2$. However as $n$ grows, the selective test shoes significantly more power than Gupta and Nagel's test.

\begin{figure}[htbp]
\begin{center}
\includegraphics[width = \textwidth]{plotMultinomialPower}
\end{center}
\caption{Power curves as a function of $\delta$. The plots in the first row all have $m = 50$ and the second row $m = 250$. The solid line is the power for the selective test and the dashed line Gupta and Nagel's test.}
\label{fig:power}
\end{figure}

@@

We would like to extend the result from multinomials to exponential families. We henceforth focus on exponential distribution taking the form
\begin{equation}
X \sim \exp\left(\theta_1 X_1 + \cdots + \theta_n X_n\right) g\left(X\right) h\left(\theta\right).
\label{eqn:exp_family}
\end{equation}
It is reasonable to assume that the family is ``symmetric'', i.e.\ if $\theta_j = \theta_k$, then the probability distribution remains the same when $X_j$ and $X_k$ are swapped. This corresponds to requiring $g\left(X\right)$ to be symmetric. We would also like to introduce a fairly mild additional condition that $g$ is {\em Schur-concave}. But first we define the notion of {\em majorization}.

@@

Suppose $X_2 < M_{13}$, then we can re-parametrize the integrals above to give
\begin{align*}
p_{12} & = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_0^\infty g\left(M_{12} + z, M_{12} - z, X_3\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz}{\int_{-D_{12}}^\infty g\left(X_1 + z, X_2 - z, X_3\right) \,dz} \\
p_{13} & = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_0^\infty g\left(M_{13} + z, X_2, M_{13} - z\right) \,dz} \\
& = \frac{\int_0^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}{\int_{-D_{13}}^\infty g\left(X_1 + z, X_2, X_3 - z\right) \,dz}
\end{align*}
To help see the re-parametrization, each of these integrals can be thought of in terms integrals along segments and rays. For example $p_{12}$ can be represented in terms integrals $A$ and $B$ in \Cref{fig:p-value}. Specifically,
$$p_{12} = \frac{B}{A + B}$$

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, above right] {$B$};
	\fill (A) circle(2pt) node[above left] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[above right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick, ->] (0, 0) -- (1, 0) node[right] {\tiny $\left(1, 0, 0\right)$};
	\draw[thick, ->] (0, 0) -- (120:1) node[above] {\tiny $\left(0, 1, 0\right)$};
	\draw[thick, ->] (0, 0) -- (240:1) node[below] {\tiny $\left(0, 0, 1\right)$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray. The diagram is drawn a level set of $x_1 + x_2 + x_3$. The yellow region represents the selection event $A_1$.}
\label{fig:p-value}
\end{figure}

\Cref{fig:compare_rays} have both the $p$-values shown on the same diagram. Proving $p_{12} \ge p_{13}$ is the same as proving
$$\frac{B}{A+B} \ge \frac{D}{C+D} ~~~~ \Longleftrightarrow ~~~~ \frac{B}{A} \ge \frac{D}{C}.$$
We will prove so be extending $A$ to include $A^*$ on the diagram. We denote the sum as $A'$. Formally,
\begin{equation}
A' = \int_{-D_{13}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz \ge \int_{-D_{12}}^0 g\left(X_1 + z, X_2 - z, X_3\right) \,dz = A.
\label{eqn:int_extension}
\end{equation}
It is thus sufficient to show that $B \ge D$ and $C \ge A'$.

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\fill[yellow!50] (0, 0) -- (C1) -- ($(C1) + (7, 0)$) -- ($(C2) + (8, 0)$) -- (C2) -- cycle;
	\node[above left] at ($(C2) + (8, 0)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick, ->] (B) -- ++(330:5) node[midway, below left] {$B$};
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick, ->] (B) -- ++(30:5) node[midway, above left] {$D$};
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The $p$-value $p_{12}$ can be written in terms of integral $A$ along the segment and $B$ along the ray; and $p_{13}$ in terms of $C$ and $D$. $A'$ would refer to the sum of $A$ with the dashed line portion labeled as $A^*$, formally explained in \Cref{eqn:int_extension}. The majorization relation is indicated by the dotted line.}
\label{fig:compare_rays}
\end{figure}

Indeed from the second point \Cref{lma:two_properties} we have
$$\left(X_1 + z, X_2 - z, X_3\right) \succeq \left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$ and the majorization reversed for $z \ge 0$. This majorization relation is indicated as the dotted line in \Cref{fig:compare_rays}. So Schur-concavity shows that
$$g\left(X_1 + z, X_2 - z, X_3\right) \le g\left(X_1 + z, X_2, X_3 - z\right)$$
for $z \le 0$, and the inequality reversed for $z \ge 0$. Taking integrals on both sides yields the desired inequality.

@@

The same argument in \Cref{fig:compare_rays} shows that $p_{12} \ge p_{13}$. This is again true for the case where $X_2 \ge M_{13}$ as well. This means that the bound can be constructed considering only $p_{12}$.

@@

\begin{figure}[htbp]
\begin{center}
\begin{tikzpicture}
	\coordinate (C1) at (60:5);
	\coordinate (C2) at (300:3);
	\coordinate (A) at (60:3);
	\coordinate (B) at ($(A) + (330:3)$);
	\coordinate (C) at ($(0, 0)!(B)!(C2)$);
	\coordinate (D) at ($(A) + (150:1)$);
	\coordinate (C3) at ($(B) + (330:5)$);
	\coordinate (C4) at ($(B) + (30:5)$);
	\coordinate (C5) at ($(C3)!(C1)!(C4)$);
	\coordinate (C6) at ($(C3)!(C2)!(C4)$);
	\draw[dashed] (0, 0) -- (C1);
	\draw[dashed] (0, 0) -- (C2);
	\draw[dashed] (C5) -- (C6) node[midway, above, rotate = -90] {Truncation for $X_j < X_{j-1}$};
	\fill[yellow!50] (0, 0) -- (C1) -- (C5) -- (C6) -- (C2) -- cycle;
	\node[above] at ($(C2)!0.7!(C6)$) {$A_1$};
	\draw[thick] (A) -- (B) node[midway, above right] {$A$};
	\draw[thick] (B) -- (C3) node[midway, below left] {$B$};
	\fill (C3) circle(2pt);
	\fill (A) circle(2pt) node[above right] {$\left(M_{12}, M_{12}, X_3\right)$};
	\fill (B) circle(2pt) node[right] {$\left(X_1, X_2, X_3\right)$};
	\draw[thick] (C) -- (B) node[midway, below right] {$C$};
	\node[below] at (C) {$\left(M_{13}, X_2, M_{13}\right)$};
	\draw[thick] (B) -- (C4) node[midway, above left] {$D$};
	\fill (C4) circle(2pt);
	\fill ($(0, 0)!(B)!(C2)$) circle(2pt);
	\draw[thick, dashed] (A) -- (D) node[midway, below left] {$A^*$};
	\fill (D) circle(2pt) node[above] {$\left(M_{13}, X_2 + D_{13}, X_3\right)$};
	\draw[thick, dotted] (C) -- (D) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] (A) -- ++(0, -3) node[midway, below, rotate=-90] {$\succeq$};
	\draw[thick, dotted] ($(B) + (30:4)$) -- ($(B) + (330:4)$) node[midway, below, rotate=-90] {$\succeq$};
\end{tikzpicture}
\end{center}
\caption{The two $p$-values constructed corresponds to taking integrals of $g$ along these segments, that lie on a level set of $x_j + x_{j+1} + x_k$. The dashed line corresponds to extension in \Cref{eqn:int_extension}. The dotted line on the far right is the truncation that enforces $X_j < X_{j-1}$.}
\label{fig:crop_rays}
\end{figure}

Here we are only comparing $X_j$ to $X_{j+1}$ by \Cref{sec:exponential_families}. The upper truncation for $X_j$ can be represented by cropping \Cref{fig:compare_rays} along a vertical line, shown in \Cref{fig:crop_rays}, thus the proof of \Cref{thm:main_result} on sufficiency to compare $X_1$ and $X_2$ remains valid with appropriate conditioning. Again we can construct the $p$-values as in \Cref{eqn:p1j} for $k>j$.

@@

\item Multinomial distribution, e.g.\ the Iowa Republican poll example in \Cref{sec:introduction}.
$$p\left(x\right) \propto \exp\left(x^T \left(\log \pi\right)\right) \frac{1_{\left\{x_1 + \cdots + x_n = m\right\}}}{x_1! \cdots x_n!}$$
Comparing $\pi_i$ is the same $\log \pi_i$, the natural parameters. Note that the multinomial coefficient is naturally Schur-concave. The step-down procedure is applied to verify the position of the other candidates. Note that for a multinomial distribution, the conditioning \Cref{eqn:step_down_law} is equivalent to conditioning only on $M_{j\left(j+1\right)}$. We summarize the test in \Cref{tbl:poll_analysis}.
